Simulating High-Dimensional Multivariate Data

### 2021-03-01 040-monte-carlo-evaluation.Rmd
fixed breaks on fig 5

dat_long %>%
    filter(Dimensions %in% c(1000, 2500, 5000, 10000, 20000)) %>%
    mutate(`Time (minutes)` = Time / 60) %>%
    ggplot(aes(Correlation, `Time (minutes)`, fill=Step)) +
    geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = myColors ) +
    scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30),
                     minor_breaks = NULL) +
    facet_grid(. ~ Dimensions) +
    theme(axis.text.x = element_text(angle = -90))
```

>>>>

dat_long %>%
    filter(Dimensions %in% c(1000, 2500, 5000, 10000, 20000)) %>%
    mutate(`Time (minutes)` = Time / 60) %>%
    ggplot(aes(Correlation, `Time (minutes)`, fill=Step)) +
    geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = myColors ) +
    scale_y_continuous(breaks = seq(0, 80, 10),
                     minor_breaks = NULL) +
    facet_grid(. ~ Dimensions) +
    theme(axis.text.x = element_text(angle = -90))
```
